Quantifying the rock-paper-scissors effect

### 2023-11-01 inst/carcinoma.Rmd
consistentification

---
title: "Analysing a carcinoma dataset with the hyper2 package"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: jss_hyper3.bib
---

@@

To cite the `hyper2` package in publications, please use @hankin2017a
(takes maybe twenty minutes to run without cache.  The value of
`carcinoma_maxp` is calculated separately [discussed below], and that
takes a few days to run).

>>>>

---
title: "Analysing a carcinoma dataset with the hyper2 package"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib
---

@@

To cite the `hyper2` package in publications, please use @hankin2017
(takes maybe twenty minutes to run without cache.  The value of
`carcinoma_maxp` is calculated separately [discussed below], and that
takes a few days to run).

### 2023-11-01 inst/cook_repeated.Rmd
consistentification

---
title: "Judging domestic cooking ability: repeated incomplete rank observations"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: jss_hyper3.bib
---

@@

To cite the `hyper2` package in publications, please use @hankin2017a;
takes about five minutes without cache.  Suppose there are five people
in a family.  Each day for five days, one person cooks a meal.  After
the fifth day, each person considers the four meals cooked by other
family members, and puts them in order of preference.  This process is
repeated and here I consider how to interpret such data.

>>>>

---
title: "Judging domestic cooking ability: repeated incomplete rank observations"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib
---

@@

To cite the `hyper2` package in publications, please use @hankin2017;
takes about five minutes without cache.  Suppose there are five people
in a family.  Each day for five days, one person cooks a meal.  After
the fifth day, each person considers the four meals cooked by other
family members, and puts them in order of preference.  This process is
repeated and here I consider how to interpret such data.

### 2023-11-01 inst/eurodance.Rmd
consistentification

---
title: "Eurovision **Dance** Contest 2008"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: jss_hyper3.bib
---

@@

To cite the `hyper2` package in publications, please use @hankin2017a;
takes about 20 minutes to process without cache.  The file
`eurodance2008.txt`, used below, is copied from "Eurovision Dance
Contest 2008", Wikipedia, accessed March 31, 2021.  First we specify
the matrix as appearing in the Wikipedia page:

>>>>

---
title: "Eurovision **Dance** Contest 2008"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib
---

@@

To cite the `hyper2` package in publications, please use @hankin2017;
takes about 20 minutes to process without cache.  The file
`eurodance2008.txt`, used below, is copied from "Eurovision Dance
Contest 2008", Wikipedia, accessed March 31, 2021.  First we specify
the matrix as appearing in the Wikipedia page:

### 2023-11-01 inst/global_liveability_ranking.Rmd
consistentification

---
title: "Global liveability ranking"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: jss_hyper3.bib
---

@@

To cite the `hyper2` package in publications, please use @hankin2017a;
takes about an hour to process without cache.

>>>>

---
title: "Global liveability ranking"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib
---

@@

To cite the `hyper2` package in publications, please use @hankin2017;
takes about an hour to process without cache.

### 2023-11-01 inst/home_advantage.Rmd
consistentification

---
title: "Quantifying the home ground advantage with `hyper2` objects"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: jss_hyper3.bib
---

@@

To cite the `hyper2` package in publications, please use @hankin2017a
(takes about fifteen minutes to run without cache).  Here I analyse a
small synthetic dataset for home ground advantage, then go on to
discuss a dataset presented by Agresti.  But first, the smallest
nontrivial example is a 2x2 case:

>>>>

---
title: "Quantifying the home ground advantage with `hyper2` objects"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib
---

@@

To cite the `hyper2` package in publications, please use @hankin2017
(takes about fifteen minutes to run without cache).  Here I analyse a
small synthetic dataset for home ground advantage, then go on to
discuss a dataset presented by Agresti.  But first, the smallest
nontrivial example is a 2x2 case:

### 2023-11-01 inst/kka.Rmd
consistentification

---
title: "A Bradley-Terry analysis of three grandmasters: Karpov, Kasparov, Anand"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: jss_hyper3.bib
---

@@

To cite the `hyper2` package in publications, please use @hankin2017a;
this `Rmd` file takes about 45 minutes to process without cache.  Here
we define dataset `kka` which is the observed scorelines between
players Karpov, Kasparov, and Anand.  It is used to calculate
likelihood functions: `karpov_kasparov_anand`, `kka_3whites` and
`kka_3draws`.  This Rmd file supercedes files
`inst/karpov_kasparov_anand.R` and `inst/kka_3draws.R` and
`inst/kka_array.R`.  Some more detail is given in `man/kka.Rd`.

>>>>

---
title: "A Bradley-Terry analysis of three grandmasters: Karpov, Kasparov, Anand"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib
---

@@

To cite the `hyper2` package in publications, please use @hankin2017;
this `Rmd` file takes about 45 minutes to process without cache.  Here
we define dataset `kka` which is the observed scorelines between
players Karpov, Kasparov, and Anand.  It is used to calculate
likelihood functions: `karpov_kasparov_anand`, `kka_3whites` and
`kka_3draws`.  This Rmd file supercedes files
`inst/karpov_kasparov_anand.R` and `inst/kka_3draws.R` and
`inst/kka_array.R`.  Some more detail is given in `man/kka.Rd`.

### 2023-11-01 inst/loser.Rmd
consistentification

---
title: "Weakly informative observations: identifying the weakest player"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: jss_hyper3.bib
---

@@

To cite the `hyper2` package in publications, please use @hankin2017a;
see also `inst/notthewinner.Rmd`.  Here we consider a situation in
which we make only a rather uninformative observation: namely, the
identity of the _loser_ (which is here taken to be me, player `a`).
We have six competitors `a,b,c,d,e,f` with nonnegative strengths
$p_1,p_2,p_3,p_4,p_5,p_6, \sum p_i=1$.  Competitor `a` has strength
$p_1$, and loses.  We are interested in how informative this
observation is with regard to various assertions about the strength of
`a`.  We have three hypotheses:

>>>>

---
title: "Weakly informative observations: identifying the weakest player"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib
---

@@

To cite the `hyper2` package in publications, please use @hankin2017;
see also `inst/notthewinner.Rmd`.  Here we consider a situation in
which we make only a rather uninformative observation: namely, the
identity of the _loser_ (which is here taken to be me, player `a`).
We have six competitors `a,b,c,d,e,f` with nonnegative strengths
$p_1,p_2,p_3,p_4,p_5,p_6, \sum p_i=1$.  Competitor `a` has strength
$p_1$, and loses.  We are interested in how informative this
observation is with regard to various assertions about the strength of
`a`.  We have three hypotheses:

### 2023-11-01 inst/monster_vs_lambda.Rmd
consistentification

---
title: "Monster or Lambda?  A likelihood analysis"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: jss_hyper3.bib
---

@@

To cite the `hyper2` package in publications, please use @hankin2017a;
takes about an hour to process without cache.  Here I consider
pairwise comparisons with a home-ground advantage and wish to compare
two likelihood functions.  First, the monster parametrization:

>>>>

---
title: "Monster or Lambda?  A likelihood analysis"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib
---

@@

To cite the `hyper2` package in publications, please use @hankin2017;
takes about an hour to process without cache.  Here I consider
pairwise comparisons with a home-ground advantage and wish to compare
two likelihood functions.  First, the monster parametrization:

### 2023-11-01 inst/rock_paper_scissors_monster.Rmd
consistentification

---
title: "Quantifying the rock-paper-scissors effect"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: jss_hyper3.bib
---

@@

To cite the `hyper2` package in publications, please use @hankin2017a;
takes about an hour to run without cache.  Here I use the `hyper2`
package to quantify the strength of a circular rock-paper-scissors
effect using the `hyper2` package, improving on previous results
[@west2008] which merely established its existence.  I use two
datasets, a three-player scoreline and a synthetic dataset referring
to wear on a seven-tooth gear wheel.

>>>>

---
title: "Quantifying the rock-paper-scissors effect"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib
---

@@

To cite the `hyper2` package in publications, please use @hankin2017;
takes about an hour to run without cache.  Here I use the `hyper2`
package to quantify the strength of a circular rock-paper-scissors
effect using the `hyper2` package, improving on previous results
[@west2008] which merely established its existence.  I use two
datasets, a three-player scoreline and a synthetic dataset referring
to wear on a seven-tooth gear wheel.
